Side-effects

### 2021-08-11 analysis/side-effects.Rmd
Remove \hline from SE tables

```{r}
left_join(
  rename(sum_sites_classes, site_n=n, site_p=p),
  rename(sum_funs_classes, fun_n=n, fun_p=p)
) %>%
  mutate(
    o=if_else(classes=="multiple", 0L, site_n),
    classes=if_else(classes=="multiple", "\\emph{multiple}", classes),
    fun_n=replace_na(fun_n, "0"),
    fun_p=replace_na(fun_p, "0\\%"),
  ) %>%
  arrange(desc(o)) %>%
  select(-o) %>%
  xtable(
    align="llrrrr"
  ) %>%
  print(
    file=file.path(TAGS_DIR, "table-se-target-envs.tex"),
    comment=FALSE, 
    include.colnames=FALSE,
    include.rownames=FALSE,
    only.contents=TRUE,
    sanitize.text.function=identity,
    timestamp=FALSE
  )
```

@@

left_join(
  select(event, event, n_event=n, p_event=p),
  select(event_calls, event, n_call=n, p_call=p),
  by="event"
) %>%
  left_join(
    select(event_site, event, n_site=n, p_site=p),
    by="event"
  ) %>% 
  mutate(event=case_when(
    event=="def" ~ "definition",
    event=="asn" ~ "update",
    event=="rvl" ~ "removal"
  )) %>%
  mutate_if(is.double, ~fmt(., suffix="%", digit=0)) %>%
  mutate_if(is.integer, ~fmt(.)) %>%
  xtable(
    align="llrrrrrr"
  ) %>%
  print(
    file=file.path(TAGS_DIR, "table-se-types.tex"),
    comment=FALSE, 
    include.colnames=FALSE,
    include.rownames=FALSE,
    only.contents=TRUE,
    timestamp=FALSE
  )
```

>>>>

```{r}
left_join(
  rename(sum_sites_classes, site_n=n, site_p=p),
  rename(sum_funs_classes, fun_n=n, fun_p=p)
) %>%
  mutate(
    o=if_else(classes=="multiple", 0L, site_n),
    classes=if_else(classes=="multiple", "\\emph{multiple}", classes),
    fun_n=replace_na(fun_n, "0"),
    fun_p=replace_na(fun_p, "0\\%"),
  ) %>%
  arrange(desc(o)) %>%
  select(-o) %>%
  xtable(
    align="llrrrr"
  ) %>%
  print(
    file=file.path(TAGS_DIR, "table-se-target-envs.tex"),
    comment=FALSE, 
    hline.after=NULL,
    include.colnames=FALSE,
    include.rownames=FALSE,
    only.contents=TRUE,
    sanitize.text.function=identity,
    timestamp=FALSE
  )
```

@@

left_join(
  select(event, event, n_event=n, p_event=p),
  select(event_calls, event, n_call=n, p_call=p),
  by="event"
) %>%
  left_join(
    select(event_site, event, n_site=n, p_site=p),
    by="event"
  ) %>% 
  mutate(event=case_when(
    event=="def" ~ "definition",
    event=="asn" ~ "update",
    event=="rvl" ~ "removal"
  )) %>%
  mutate_if(is.double, ~fmt(., suffix="%", digit=0)) %>%
  mutate_if(is.integer, ~fmt(.)) %>%
  xtable(
    align="llrrrrrr"
  ) %>%
  print(
    file=file.path(TAGS_DIR, "table-se-types.tex"),
    comment=FALSE, 
    hline.after=NULL,
    include.colnames=FALSE,
    include.rownames=FALSE,
    only.contents=TRUE,
    timestamp=FALSE
  )
```
